---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Install the latest version of qualtr

```{r}
devtools::install_github("context-dependent/qualtr")

library(qualtr)
```

## Encrypt configuration details in package root

Other packages ask you to store sensitive configuration details in unencrypted yaml files. While this offers the obvious convenience of not requiring a password, it is insufficiently secure for our needs. `encrypt_conf` asks for your api_token, datacentre url, and key. It saves these details locally in an encrypted .rds file in the package root folder. Run the following chunk in the console, replacing the capitalized parameters with your account's details

```{r}

encrypt_conf(
  api_token = API_TOKEN,
  base_url = BASE_URL, 
  key = PASSWORD
)

```

## Confirm your saved configuration details by decrypting them

`decrypt_conf` is used internally to decrypt your configuration details, stored locally in .conf.rds in the package root. You can call it at the top level to confirm that the credentials are successfully stored. 

```{r}
decrypt_conf()
```

